SunPy - Python for Solar Physics

### 2014-01-30 3-2-HEK.tex
more lightish editing

The Sun is an active star and exhibits a wide range of transient phenomena 
(e.g., flares and radio bursts) on many different time-scales, length-scales and 
wavelengths. Observations and metadata concerning these phenomena are collected 
in the Heliophysics Event Knowledgebase (HEK) \citep{hek2012}.  Entries are generated both by 
automated algorithms and human observers.  Some of the information in the HEK 
reproduces feature and event data from elsewhere (for example, the \textit{GOES} flare catalogue),
and some is generated by the Solar Dynamics Observatory Feature Finding Team 
\citep{martens2012}.  The advantage of the HEK is it 
provides an homogeneous and well-described interface to a large amount of 
feature and event information of interest to the solar physics community.

SunPy accesses this information through the \texttt{hek} module, which was
developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
use of the 
\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{HEK
 API}.
The current list of events maintained by the HEK and their properties can be 
found at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.

Simple HEK queries consist of start time, an end time, and an event type 
(Listing \ref{code:hek:simple}). Event types are specified as upper case, 
two letter strings, and are 
identical to the two letter abbreviations found at the HEK website, 
\url{http://www.lmsal.com/hek/VOEvent_Spec.html}.

@@

HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
returns flares west of 50 arcseconds or those that have a peak flux above 
1000.0 (the units of the flux are FRM-dependent and are described at the HEK 
website).
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType('FL'),
...                       (hek.attrs.Event.Coord1 > 50) 
...                       or (hek.attrs.FL.PeakFlux > 1000.0))
\end{minted}
\caption{HEK query using the logical \texttt{or} operator.}
\label{code:hek:or}
\end{listing}
All FRMs report the required feature attributes (as described at 
\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
are FRM dependent.  If a FRM does not have one of the optional attributes, 
\texttt{None} is returned by the \texttt{hek} module.

>>>>

The Sun is an active star and exhibits a wide range of transient phenomena 
(e.g., flares, radio bursts) on many different time-scales, length-scales and 
wavelengths. Observations and metadata concerning these phenomena are collected 
in the Heliophysics Event Knowledgebase (HEK) \citep{hek2012}.  Entries are generated both by 
automated algorithms and human observers.  Some of the information in the HEK 
reproduces feature and event data from elsewhere (for example, the \textit{GOES} flare catalogue),
and some is generated by the Solar Dynamics Observatory Feature Finding Team 
\citep{martens2012}.  The advantage of the HEK is it 
provides an homogeneous and well-described interface to a large amount of 
feature and event information of interest to the solar physics community.

SunPy accesses this information through the \texttt{hek} module, which was
developed with support from ESA's SOCIS 2011.  The \texttt{hek} module makes 
use of the 
HEK API\footnote{For more information see 
\href{\href{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}{http://vso.stanford.edu/hekwiki/ApplicationProgrammingInterface?action=print}}.
The current list of events maintained by the HEK and their properties can be 
found at \url{http://www.lmsal.com/hek/VOEvent_Spec.html}.

Simple HEK queries consist of start time, an end time, and an event type 
(Listing \ref{code:hek:simple}). Event types are specified as upper case, 
two letter strings, and are 
identical to the two letter abbreviations found at the HEK website, 
\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}

@@

Similar to the \texttt{vso} module, HEK comparisons can be combined using Python's logical operators (e.g., \texttt{and}
and \texttt{or}). This makes complex queries easy to create: Listing \ref{code:hek:or} 
returns flares west of 50 arcseconds or those that have a peak flux above 
1000.0 (the units of the flux are FRM-dependent and are described at the HEK 
website).
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType('FL'),
...                       (hek.attrs.Event.Coord1 > 50) 
...                       or (hek.attrs.FL.PeakFlux > 1000.0))
\end{minted}
\caption{HEK query using the logical \texttt{or} operator.}
\label{code:hek:or}
\end{listing}
All FRMs report the required feature attributes (as described at 
\url{http://www.lmsal.com/hek/VOEvent_Spec.html}), but the optional attributes 
are FRM dependent.  If a FRM does not have one of the optional attributes, 
\texttt{None} is returned by the \texttt{hek} module.
